Scale Space Edge Detection

### 2018-03-10 paper.tex
updated

$\mathcal G_\gamma L$ represents the normalized gradient magnitude, which serves as our edge strength measure, $\partial_t(\mathcal G_\gamma L)$ represents the first partial of $\mathcal G_\gamma L$ with respect to the scale parameter as described in (Eq. \ref{Gl})
and $\partial_{tt}(\mathcal G_\gamma L)$ represents the inverted sign of the second partial of $\mathcal G_\gamma L$ with respect to scale.
These definitions describe the local maxima of of the edge strength with respect to the scale parameter.

>>>>

$\mathcal G_\gamma L$ represents the normalized gradient magnitude, which serves as our edge strength measure, $\partial_t(\mathcal G_\gamma L)$ represents the first partial of $\mathcal G_\gamma L$ with respect to the scale parameter as described in (Eq. \ref{dtGl})
and $\partial_{tt}(\mathcal G_\gamma L)$ represents the inverted sign of the second partial of $\mathcal G_\gamma L$ with respect to scale.
These definitions describe the local maxima of of the edge strength with respect to the scale parameter.
